\documentclass{article}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage{listings}
\title{On the Encounter with the Parking Lot Junkies}
\author{Varik Valefor\\{\small \texttt{$<$varikvalefor@aol.com$>$}}}
\date{TODO\@: RECALL DATE!}
\begin{document}
	\maketitle
	\section{Executive Summary}
		Some possible junkies drive an excessively-large-spoilered car to
		a gas station.

		VARIK arrives and sees the car and junkies.

		After VARIK arrives, one possible junkie exits the vehicle and
		brushes the teeth of this junkie.

		VARIK eventually paces near VARIK's rental car and laughs
		hysterically.

		The junkies leave.  The sound of the junkies' car
		resembles the sound of a wet fart.
	\section{Definitions}
		$D$ denotes the rental car of VARIK's party.
	\section{Arriving at the Gas Station}
		Whilst taking a vacation, VARIK and VARIK's driver are in Moab,
		US-UT\@.

		VARIK's driver wishes to urinate and parks $D$ at a nearby gas
		station.
	\section{Description of Possible Junkies}
		A man $k$ exits a BMW car and brushes $k$'s teeth
		in the parking lot of the gas station.  Another man continues to sit
		within this car.

		VARIK jokingly states that these men are likely ``freakin' parking
		lot junkies''.

		After making this statement, VARIK notices that the spoiler of the
		BMW car is unusually large, having a height of approximately 0.5
		metres.

		VARIK and VARIK's driver walk toward the gas station with the intent
		of using this gas station's toilets.  VARIK's driver locks the doors
		of $D$.

		VARIK forgets to remove VARIK's face mask from $D$.

		VARIK returns to the now-locked $D$ before attempting and failing
		to open the door of $D$.
	\section{Pacing near the Rental Car}
		After returning to $D$, VARIK begins to pace near $D$.

		After pacing for approximately one (1) minute, VARIK assumes that
		drivers who see VARIK whilst VARIK is pacing may assume that VARIK
		is another ``freakin' parking lot junkie.''

		The irony of VARIK's situation amuses VARIK\@.  VARIK begins to
		chuckle.

		VARIK's chuckling becomes hysterical laughter.
	\section{Leaving}
		VARIK's driver returns to $D$.

		VARIK fetches VARIK's mask, uses the toilet of the gas station, and
		re-enters $D$.

		VARIK's party leaves the gas station as the BMW car leaves the gas
		station.

		The BMW car accelerates loudly.

		VARIK finds that the sound of this BMW car resembles the sound of
		the typical ``wet fart''.
\end{document}
